\begin{acknowledgements}
First, I would like to acknowledge my mom and dad for teaching me the values of curiosity, persistence, dedication, honesty, and hard work, and for their immense support and love throughout the highs and lows of my academic career. I would also like to acknowledge my teachers, especially my 1\textsuperscript{st} grade teacher Ms.\ Beth Vanderson for kindling my interest in science early, and Ms.\ Theresa Bowser and Ms.\ Shannon Roof in high school AP Biology for exposing me to the elaborate splendor of the life sciences.

I would like to thank my research colleagues and mentors along the way. I am grateful to Dr.\ Victor Jin for introducing me to the field of bioinformatics and the research opportunities he provided me as an undergraduate, and also his students Dr.\ Xun Lan and Brian Kennedy for showing me the ropes of NGS\@. I would also like to acknowledge Dr.\ Richard Lifton, both for the opportunity of the HHMI Summer Med Fellowship and for the chance to learn about working with large-scale data sets. I am especially grateful for my colleagues and mentors in the Roychowdhury lab. I would like to acknowledge Jharna Miya, Dr.\ Eric Samorodnitsky, and Dr.\ Anoosha Paruchuri for expanding my technical horizons in computational biology. I am thankful to Drs.\ Melanie Krook, Julie Reeser, Michele Wing, and Hui-Zi Chen for their advice, support and mentorship, and I wish to acknowledge Amy Smith, Dorrelyn Martin, and Thuy Dao for generating sequencing data. In addition, I am grateful to my PhD classmates in the 2016 BSGP entering class for much shared learning and stimulating discussion.

I would especially like to thank Dr.\ Sameek Roychowdhury for his invaluable mentorship and support throughout my PhD journey. I am truly grateful for his exceptional vision in translational research, which has inspired me to seek to become a physician scientist. I am particularly grateful for the value he has placed on teamwork, collaboration, and continued professional development, and for putting patients first in his research and clinical practice. I wish to acknowledge my PhD committee members; Dr.\ Lianbo Yu for his technical and statistical guidance, Dr.\ Ewy Math\'e for the opportunity of a research rotation and her insights into my research, Dr.\ Robert Baiocchi for his perspective as a molecular biologist and a hematologist, and Dr.\ Lang Li for his extensive bioinformatics expertise. Also, I would like to thank Dr.\ Roychowdhury's collaborators, especially Drs.\ Patricia Allenby and Diana Thomas for facilitating his rapid research autopsy study and Dr.\ Aharon Freud for pathology services. Finally, I would like to acknowledge the patients of Dr.\ Roychowdhury and their families, especially those who have given the gift of body donation so that others may one day benefit, and those whom I have had the privilege to meet; their daily fight against cancer continually inspires me in my pursuit of cancer research.

Previously copyrighted materials utilized with permission in this text are acknowledged at first appearance.
\end{acknowledgements}
