\begin{vita}

\dateitem{January 28, 1991}{Born --- Columbus, Ohio, USA}

\dateitem{2013}{B.S. Health and Rehabilitation Sciences}

\dateitem{2016-present}{Graduate Fellow,\\
			 The Ohio State University.}


\begin{publist}

%% UPDATE FOR 2010:
%  Grad school only wants research publications, and it only wants those
%  research pubs that are actually published. Accepted or ``to appear''
%  publications don't count. If they look closely, they'll tell you to
%  remove any publications that aren't in print. Haivng said that, they
%  probably won't look that closely unless you put a really long list
%  here. You're tempting fate if you add instructional publications
%  though.

\researchpubs

\begin{itemize}
    \item Bonneville R, Paruchuri A, Wing MR, Krook MA, Reeser JW, Chen HZ, Dao T, Samorodnitsky E, Smith AM, Yu L, Nowacki N, Chen W, Roychowdhury S\@. Characterization of clonal evolution in microsatellite unstable metastatic cancers through multiregional tumor sequencing. \textit{Molecular Cancer Research} 2021, 19(3):465--74. PMID: \pmid{33229401}.
    \item Paruchuri A\cofirst, Chen HZ\cofirst, Bonneville R, Reeser JW, Wing MR, Krook MA, Samoroditsky E, Miya J, Dao T, Smith AM, Freud AG, Allenby P, Roychowdhury S\@. Research autopsy demonstrates polyclonal acquired resistance in a patient with metastatic gastrointestinal stromal tumor. \textit{JCO Precision Oncology} 2020 [Epub 3 Mar 2020]. PMID: \pmid{32923900}.
    \item Krook MA\cofirst, Bonneville R\cofirst, Chen HZ, Reeser JW, Wing MR, Martin D, Smith AM, Dao T, Samorodnitsky E, Paruchuri A, Miya J, Baker KR, Yu L, Timmers C, Dittmar K, Freud AG, Allenby P, Roychowdhury S\@. Tumor heterogeneity and acquired drug resistance in FGFR2 fusion-positive cholangiocarcinoma through rapid research autopsy. \textit{CSH Molecular Case Studies} 2019, 5:a004002. PMID: \pmid{31371345}.
    \item Krook MA, Barker H, Chen HZ, Reeser JW, Wing MR, Martin D, Smith AM, Dao T, Bonneville R, Samorodnitsky E, Miya J, Freud AG, Monk JP, Clinton SK, Roychowdhury S\@. Characterization of a KLK2-FGFR2 fusion gene in two cases of metastatic prostate cancer. \textit{Prostate Cancer and Prostatic Diseases} 2019 [Epub 1 May 2019]. PMID: \pmid{31043681}.
    \item Chen HZ\cofirst, Bonneville R\cofirst, Yu L, Wing MR, Reeser JW, Krook MA, Miya J, Samorodnitsky E, Smith AM, Martin D, Dao T, Guo Q, Liebner D, Freud AG, Allenby P, Roychowdhury S\@. Genomic characterization of metastatic ultra-hypermutated interdigitating dendritic cell sarcoma through rapid research autopsy. \textit{Oncotarget} 2019, 10(3):277--88. PMID: \pmid{30719225}.
    \item Krook MA\cofirst, Chen HZ\cofirst, Bonneville R\cofirst, Allenby P, Roychowdhury S\@. Rapid research autopsy: piecing the puzzle of tumor heterogeneity. \textit{Trends in Cancer} 2019, 5(1):1--5. PMID: \pmid{30616752}. Review.
    \item Chen HZ, Bonneville R, Roychowdhury S\@. Implementing precision cancer medicine in the genomic era. \textit{Seminars in Cancer Biology} 2018, S1044--579X(17):30232--8. PMID: \pmid{29857039}. Review.
    \item Siddiqui JK, Baskin E, Liu M, Cantemir-Stone CZ, Zhang B, Bonneville R, McElroy JP, Coombes KR, Math\'e EA\@. IntLIM: Integration using linear models of metabolomics and gene expression data. \textit{BMC Bioinformatics} 2018, 19(1):81. PMID: \pmid{29506475}.
    \item Bonneville R\cofirst, Krook MA\cofirst, Kautto EA, Miya J, Wing MR, Chen HZ, Reeser JW, Yu L, Roychowdhury S\@. Landscape of microsatellite instability across 39 cancer types. \textit{JCO Precision Oncology} 2017 [Epub 3 Oct 2017]. PMID: \pmid{29850653}.
    \item Kautto E, Bonneville R, Miya J, Yu L, Krook MA, Reeser JW, Roychowdhury S\@. Performance evaluation for rapid detection of pan-cancer microsatellite instability with MANTIS. \textit{Oncotarget} 2016, [Epub 12 Dec 2016]. PMID: \pmid{27980218}.
\end{itemize}

% \instructpubs
%
% \pubitem{B.~Simpson, ed.,
% \newblock ``Lab notes for Cow Science 101'', 1909.}

\end{publist}



\begin{fieldsstudy}

% The \majorfield* uses the unit specified in the \unit command used
% earlier in your document. If you want to use a different unit, use the
% second form shown here
\majorfield*
% \majorfield{Cow and Dairy Science}

%%
%% Note:  If there were only one field of study, the following list 
%%        would best be done using the following command:
%%
%%  \onestudy{Only Topic}{Only Professor}
%%

% \begin{studieslist}
% \studyitem{Topic 1}{Prof.\ Big Dude}
% \studyitem{Topic 2}{Prof.\ Other Dude}
% \studyitem{Topic 3}{Prof.\ Another Dude}
% \end{studieslist}

\end{fieldsstudy}

\end{vita}

